Clouds and Radiation in a mock-Walker Circulation

### 2020-09-18 Silvers_WalkerCell_response2reviewers.tex

%I have responded to your annotations in the pdf file: 
%Silvers\_WalkerCell\_reviewer1\_1592417419\_response.pdf

\subsection{General Comments}

\begin{itemize}
\item Abstract: 
I think your abstract could benefit from some  reorganization/clarification. It seems to me that there are two overarching themes to your paper:
%%
    \begin{enumerate}
  \item There are significant differences between the CRM-like and GCM-simulated Walker circulation, including a stronger/more symmetric and less low clouds in the CRM-like simulations.
%% 
  \item The substantial differences in cloud type between the CRM-like and GCM-like simulations lead to substantial differences in the  atmospheric responses to the longwave cloud radiative effect (e.g. more precipitation in the GCM-like simulation, and less precipation in the CRM-like simulation). 
    \end{enumerate}
%%
    I think the abstract should summarize these points in this order to help improve the clarity.
   As it stands, you jump around between 1. and 2. and it makes it a bit more difficult to follow.

   \textcolor{blue}{We have taken your advice, mostly by moving the content from the former second to last sentence in the abstract to earlier in the abstract and rewriting lines 27-28 of 
   the originally submitted manuscript.}

@@

  \item Table 2:  This table is helpful. I wonder if adding two columns for high cloud and low cloud fraction could help further summarize some of your key results?

  \item Figure 1: Nice figure. It is interesting that the middle and right panels are so similar to each other. Does this suggest that the cloud longwave effects are weak in the E25 simulation? And potentially much too strong in the P25 simulation? It might be useful to show a plot of the longwave heating rate for each simulation...  
  \textcolor{blue}{I agree, the similarity of panels b and c is interesting.  However, I hesitate to conclude that LW CRE is very weak in E25 LWCRE-on and 
  too strong in the P25 simulation.  Mostly because I don't know what constitutes a LW CRE that is `too strong'.  I interpret the difference between panels
  a and b to indicate how important the LWCRE is to the atmospheric state, and the symmetry of panel c to indicate the more regular behavior of explicit convection.
  While panel b is much more symmetric than panel a, there are still notable asymmetries present which supports the idea that part of the asymmetry comes from the convective parameterization and part of it comes from the LWCRE. }
  \textcolor{red}{could plots of longwave heating be part of the extra section comparing E25 and P25?}

  \item Ln 282-284:  Doesn't Fig. 1 show that P25 control yields a drier atmosphere? You also state this in lines 278-280. I guess it yields a drier subsiding region, but also a much more humid convective region. 
  \textcolor{blue}{Yes, the end of your statement is correct, the subsiding region is drier, but the convective region is more humid than the other experiments.  This is stated in the lines you mention, as well as directly in lines 276-278.  It is the case that the mean values are a bit different than one might expect from looking at Fig. 1.  This also highlights the difference between the means of water vapor compared to water condensate.}

  \item Ln 310: I only see prominent asymmetry in the P25 simulations. The P100 simulation is only slightly asymmetric, and the P100L simulation not asymmetric at all.
  \textcolor{red}{The language describing this has been changed to reflect off center features, rather than just asymmetric.  Please see the discussion in the subsection which discussed 
  the comparison between P25 and E25.   While P100 is only slightly asymmetric, it is 
  consistently off center.  The asymmetry of P25L is greater than may be initially apparent because of the difference in domain size.  A similar asymmetry to the P25 case would 
  be shown with a shift off-center that appears smaller than for P25 (see Figs 5 and 8 of revised manuscript).  }

@@

  \item Ln 690-692: Can you speculate about why this might be? Could the smaller low-cloud amounts in the CRM-like experiment be due to the stronger overturning circulations, and hence stronger subsidence drying?

  \item Ln 701: 5\%
  \textcolor{blue}{Done}

  \item Ln 704: context 'of' 
  \textcolor{blue}{Done}

  \item Ln 704-706: I know this is not the focus of your study, but I wonder which simulation has the more realistic cloud profile: the CRM or GCM-like simulation? The low-cloud fraction seems quite small in the CRM-like experiments...
  \textcolor{blue}{I have added a new figure that looks at observations from the tropical Pacific in order to give a sense of how these model results compare to observations.  
  Figure 15 shows cloud fraction from the MISR instrument on board NASA's Terra satellite.  I focused on a region that is usually identified with the Walker Circulation and plotted profiles for the domain mean, a region with upwelling, and a region with downwelling.  If comparing to figure 14 in our manuscript in which we look at the cloud fraction in the subsidence 
  region it is seen that both the upper-level and low-level cloud fraction observed by MISR in the downwelling region is closer to that of the GCM-like simulations.  This is 
  somewhat surprising but it should be kept in mind that this type of comparison is very qualitative and subject to numerous caveats.  For example, impacts from the Hadley cell 
  have not been filtered out of this observational data.  I am hopefully that a quick look at data like this could help to motivate future studies in which a more detailed comparison 
  between models of the Walker Circulation and observations.  The following red text has been added to the manuscript:}

  \textcolor{red}{In order to make a qualitative connection to observed clouds and hopefully motivate a more detailed comparative study we look at the clouds observed with the MISR instrument 
  on board NASA's Terra satellite.  We use the domain (10N-35S) which was identified by Schwendike et al., 2014 as defining the regional Walker circulation in the Pacific.  
  The left panel of Figure 15 shows the cloud fraction averaged from March 2000-November 2019 of the full domain of the Pacific regional Walker circulation.  This region 
  includes much of the so-called warm pool beneath the ascending branch of the Walker Circulation as well as the eastern Pacific subsidence regions that encompass the stratocumulus
  cloud decks that are common off the west coast of South America.   To calculate profiles of the cloud fraction as a function of height we sum the MISR data over all optical depths 
  and plot the domain mean (dashed line), a region of subsidence ($10^\circ$ N-$35^\circ$S; $120^\circ$W-$60^\circ$W, solid line), and a regions that is characterized by deep 
  convection ($10^\circ$N-$35^\circ$S; $120^\circ$E-$180^\circ$, dash-dot line).  Overall, both the upper- and low-level cloud fraction from MISR are closer to the cloud profiles 
  simulated by the GCM-like models.  It would be interesting in future studies to sample the observations for time periods in which the Walker Circulation is strong}

  \item Ln 737-739: This is certainly an interesting result, but I wouldn't say it is a 'consistent asymmetry' given the results in the P100L simulation. I think this should be rephrased to reflect that.
  \textcolor{blue}{This sentence now reads: Two examples include the consistently off-center circulations, and precipitation patterns,
relative to the fixed SST pattern, and the dominance of the large-scale precipitation over the convective precipitation.}
%
\end{itemize}

@@

The manuscript offers a thorough analysis of this intricate coupling, and will undoubtedly be a significant contribution to the literature. As you will see below, the bulk of my comments relate to the organization of the manuscript, which I believe should be revisited and can be improved to present these meaningful results in a more cohesive and concise manner. In addition, I believe more attention should be given to the comparison between the two 25 km-resolution simulations: those with parameterized convection and explicit convection, respectively. While these suggested organizational edits may be more of a significant undertaking, I ultimately believe this set of revisions to be more minor, and look forward to reading the finished product!

Below, I have organized my comments into a set of general, overarching points first, followed by a handful of individual, line-by-line comments.

\subsection{GENERAL COMMENTS}
*In terms of organization, I believe some reworking and consolidation of results are useful and fairly straightforward. Some examples include:

\begin{enumerate}
  \item Section 3 is meant to focus on the impact of LWCRE, but subsequent sections frequently reference the comparison between LWCRE-on and LWCRE-off as well (i.e. lines 361-373, 398-401, 459-462).
  \textcolor{red}{During the writing I attempted consolidating the comparison between LWCRE on/off to one section but found it to create more problems than it 
  solved because the LWCRE on/off experiments have such a strong influence on all of the other sections.  You mention lines 361-373, which happens to be a 
  perfect example of the difficult.  Figures 5 and 6 illustrate the overlapping influence of the LWCRE on/off effects and domain size dependence.  
  As a result, I have chosen to largely focus on your other excellent recommendations for reworking the organization of the manuscript.}
  \item Comparisons between E25 and P25 are made in multiple sections, and some of these results are referenced in passing (i.e. lines 518-519, "It is also worth noting that in contrast to the P25 case which has strong domain shear..."). Given the importance of this resolution in the manuscript to link GCMs and CRMs, I believe that this deserves its own section.
  \textcolor{red}{To further aid in the comparison between E25 and P25, the P25 control and P25 LWCRE-off profiles have been added to Figure 11 (note the number of this figure may change depending on the E25/P25 section).  The color used to show the E25 profiles has also been changed from yellow to purple in several of the figures and I think this also helps readers to compare E25 and P25.}
  \item Figure 10, in the context of its section on resolution dependence, seems to convey a similar picture as Figure 9, and its already been well-established that removing LWCRE seems to broaden/weaken the mass circulation robustly.

@@

  \textcolor{blue}{You are right that there is some redundancy of message in Figure 10, but I think there is enough interest in the results of the 1 and 2km simulations to warrant inclusion of Figure 10. }

  \item I believe that Sections 6 and 7 can be consolidated and combined into one, given that the first half of Section 6 is already a well-constructed and well-divided summary of results.
  \textcolor{red}{related to comments from Reviewer \# 1 on reducing number of points in section 6...}
  \item In several parts of the manuscript, multiple references are made to Figures/Tables that appear 10 or more pages earlier. For ease of reading, perhaps quantities such as the domain-mean precipitation can be incorporated into the Figures. For example, Figure 2's legend can list the domain-mean precipitation values next to the labels.
  \textcolor{red}{I have added domain-mean values to the precipitation shown in Figure 3, and extended the markers at the end of the time series to make Figure 3 easier to read.  
  In response to several comments from you and the other reviewers, section 3, 6, and 7 have been somewhat reorganized and hopefully make the manuscript easier to read.}
\end{enumerate}

@@

  \textcolor{blue}{This is a good point, and I think that we have similar interests in some of what the paper has not covered.  As you could probably see in the paper, organizing the results was challenging, and interpretation was made difficult by many unexpected complications.  Based on the number of experiments which I was already trying to organize in the writing of the manuscript I chose to keep the focus of the paper rather small.   Another factor which limited the number of experiments that I could include in the paper is that I also performed a number of uninteresting or unsuccessful experiments in which various parameter settings were modified, and in which some minor changes were made in the code of the Tiedtke large scale cloud scheme.  I have more experiments than I can handle! }

  \item Have any additional simulations been conducted at resolutions between 2-25, and 25-100 km? It would be interesting to see how smooth the transition is between these two regimes of cloud distribution and radiative response, and if a specific threshold could be found, holding all other conditions equal, to significantly affect the cloud distribution.

  \textcolor{blue}{No, I have not performed experiments at other resolutions (a few at 5km, at the very beginning with different code base, but the analysis was not carried very far).  Also see answer to you comment just before this one. }

  \item Some figures are a bit difficult to read, in particular Figures 6 and 13. In particular, for Figure 6 it is difficult to compare the P25 and P25L simulations because the colors on the lines are the same. Figure 13 would be best oriented as a 2X2 window similar to Figure 12, especially given the subtle differences in the rightmost panel.
  \textcolor{red}{For several of the figures (6, 11,12, and 13) the labels and axis font size has been increased.}  
  \textcolor{blue}{Figure 6 has now been split into two figures, one
  showing results on the small/control domain size and the other showing results on the large domain.}

@@

\subsubsection{Assessing the realism of the simulated mock-Walker cell}

As the authors point out (L67), the Walker cell setup can be compared to observations from the Pacific region. As their
results show large differences between the E25/P25 and the E2/E1 simulations (e.g. L420-421), how can the reader
assess which simulation best captures the Walker cell’s hydrological cycle?
Although a direct comparison is impossible because of the idealized mock-Walker cell setup, I would highly suggest
adding observational and/or meteorological reanalysis data to at least some of Section 5’s figures (Figure 8-13) to comment
on which configuration leads to the most observationally consistent Walker cell. To facilitate the comparison, the authors
could e.g. choose a period of time where the Pacific’s zonal surface temperature gradient is in the range of the experiments
listed in Table 1 $(\Delta SST/ \Delta x = 10^{-4} - 10^{-3} K/km).  $

\subsection{Minor comments}

You will find 15 minor comments attached to the annotated PDF of the manuscript. Additional comments that apply
throughout the paper are listed below:
\begin{itemize}
  \item Labeling all figure panels using the conventional notation a/b/c/d (e.g. Figure 1, 2, etc.)
  \textcolor{blue}{Figures 1-14 now have panels labelled with a/b etc., when multiple panels are present.}

  \item Make titles more formal (e.g. Figure 13) and using a consistently large font size across figures (for instance, the
titles are easy to read in Figures 9 and 10, but not in Figures 11, 12, and 13)
  \textcolor{blue}{The font size for axis and titles in Figure 12 has been increased, x-axis label for Figure 12d corrected to read only units.}
\end{itemize}

### 2020-09-18 Silvers_WalkerCell_revision.tex
substantial additions to both Silvers_WalkerCell_response2reviewers.tex and Silvers_WalkerCell_revision.tex as part of the revisions for Silvers and Robinson, 2020

The Walker circulation connects the regions with deep atmospheric convection in the western tropical Pacific to the shallow-convection, tropospheric subsidence, and stratocumulus cloud decks of the eastern Pacific.  Although important to many elements of the Earth system such as tropical precipitation, and cloud feedback processes, interactions between large-scale tropical circulations and these cloud systems are still not well understood.   The purpose of this study is to better understand the multi-scale interactions between the Walker circulation, cloud systems, and interactive radiation.  
To do this we simulate a mock-Walker Circulation with a full-physics General Circulation Model (GCM) using idealized boundary conditions.  Our experiments use a doubly-periodic domain with grid-spacing of 1, 2, 25, and 100km.  We thus span the range from General Circulation Models (GCMs) to Cloud-system Resolving Models (CRMs).  Our model is derived from the Geophysical Fluid Dynamics Laboratory (GFDL) atmospheric GCM (AM4.0).  Our GCM-like experiments have a large low-level cloud fraction while the CRM-like experiments have more upper-level clouds.  This difference leads to opposite atmospheric responses to changes in the longwave cloud radiative effect (LWCRE).  Active LWCRE lead to increased precipitation for our GCMs, but decreased precipitation for our CRMs.  The LWCRE leads to a narrower rising branch of the circulation and substantially increases the fraction of precipitation from the large-scale cloud parameterization.  Decreasing the grid-spacing to 1km and 2km results in stronger overturning circulations, more condensate aloft, and less precipitation.    This work demonstrates that a mock-Walker circulation is a useful generalization of RCE that includes a large-scale circulation.

@@

@@

When the coupling between the circulation and clouds is broken by making the clouds invisible to the 
LW radiation, the atmospheric state is more symmetric about the maximum SST and the weaker circulation
is more spread out horizontally.   The mass streamfunction and vertical velocity both show the 
P25 (Figure \ref{fig:rh_psi_P25vsE25}, left panels; Figure \ref{fig:precip_vertvel}) experiment to have 
a stronger, more concentrated overturning circulation than either E25 (right panels) or P25 LWCRE-off (center panels).   
The control GCM\add[LGS]{-like} experiment (P25) also has higher RH and more condensate in the convective
region and a dryer subsidence region, relative to the P25 LWCRE-off and E25 experiments. 
Averaged over the full domain, the P25 case with parameterized convection results in a dryer atmosphere with less condensate (both liquid and ice). 
This default configuration in which the clouds interact with the LW radiation results in a stronger,
spatially concentrated circulation and will be discussed further in later sections (also seen Figures 4, 5, 9 and 10).
Active LWCRE leads to lower values of domain mean OLR and higher domain mean precipitable water (PW) in all cases (Table \ref{tab:experimentmeans}).

@@

One of the most prominent features of our GCM-like simulations is an asymmetry (relative to the 
symmetric SST distribution) in both the time-dependent and steady-state solutions.  
This asymmetry is particularly apparent in the P25 experiment on the small domain but is also present on larger domains and 
with a grid-spacing of $100 \, \rm{km}$ (Figures  \ref{fig:precip_vertvel}, \ref{fig:domdep} and  \ref{fig:conv_vs_ls}). 
The steady-state precipitation maximum is located  not over the warmest SST but is shifted to slightly cooler temperatures.  
This asymmetry is present in the vertical velocity, mass circulation, relative humidity, specific humidity, and radiative heating.  
In the Hovm{\"o}ller diagrams (Figures \ref{fig:domdep} and \ref{fig:domdep_lwoff}), the precipitation appears to be averse 
to residing over the SST maximum.  
For the P25 case shown in Figure \ref{fig:rh_psi_P25vsE25} a strong ($1 \, \rm{m \, s^{-1}}$) domain
mean shear develops above about 500 m which shifts the precipitation and circulation off center for years at a time.  
When the convective parameterization is turned off (E25), the overturning circulation 
becomes weaker and broader (seen in vertical velocity, and the mass streamfunction, Figures \ref{fig:rh_psi_P25vsE25} and \ref{fig:precip_vertvel}), 
and the precipitation, cloud fields, and circulation reside over the SST maximum (but only for about 1 year before the variability 
increases).    
While the parameterized convection plays a large role in driving this asymmetry, it is not purely a 
result of the convective parameterization, but also due to an interaction between the convective 
parameterization and the LWCRE.   The degree to which this asymmetry influences the comparison with other 
experiments is unclear.

\begin{figure}
  \centering
      \includegraphics[width=0.8\columnwidth]{walkerfigs/PrecipVertVelocity_LWCRE_onoff.eps}
  \caption{Precipitation (top) and vertical velocity (bottom) at approximately 530 hPa for P100, P25, E2, and E1 experiments.  
  The data have been averaged over the short horizontal dimension of the channel and over the 
  equilibrated part of the experiments.  Control configurations with default model physics are on the 
  left.  On the right are the corresponding experiments with the longwave cloud radiative effect turned
  off (LWCRE-off).}
  \label{fig:precip_vertvel}
\end{figure}
%
% below shows that the circulation extremes decrease when the lw cre is switched off.  the case with a 
% grid-spacing of 25 km shows the largest difference 
%
%% max/min values for the stream function with lwcre off:
%(0)	max/min of psiplot ensind  is: 0.3477345977293868 and: -0.2115510906212598   diff = 0.56
%(0)	max/min of psiplot1 is: 0.3195050101301776 and: -0.2795603759630235             diff = 0.60
%(0)	max/min of psiplot2 is: 0.3551683771471268 and: -0.3245916357825396             diff = 0.68
%
%% max/min values for the stream function with lwcre on:
%(0)	max/min of psiplot ensind  is: 0.1346705118433919 and: -0.6774837967222883    diff = 0.81
%(0)	max/min of psiplot1 is: 0.301707822836468 and: -0.3661587052771586                diff = 0.67
%(0)	max/min of psiplot2 is: 0.4634904466711686 and: -0.3170573366946793               diff = 0.78

@@

One of the simplest measures of convective aggregation and the large-scale circulation is the subsidence fraction (SF), the fraction of the domain 
in which the mid-tropospheric air is subsiding \cite{Coppin_Bony_2015}.  
As convection becomes more organized, or aggregated, the SF will increase.  For an overturning circulation a contraction of the convective 
region should result in a larger subsidence fraction.  
This is precisely what we see in Table \ref{tab:experimentmeans}.  For each of our experiments with LWCRE-on the SF is larger than 
or equal to the case with LWCRE-off \remove[LGS]{(with the exception of E25)}.   
While our mock-Walker circulation is distinct from radiative convective equilibrium (RCE) and the resulting spontaneous self-aggregation, our 
region of persistent deep convection clearly corresponds to a state of aggregation. 
Using a mock-Walker circulation allows one to study controlled convective aggregation rather then spontaneous convective self-aggregation. 
Previous studies have shown a dependence of aggregation 
on temperature \cite{Khairoutdinov2010, Wing2014, Cronin2017}, Table \ref{tab:experimentmeans} illustrates how much the aggregated 
state can vary among experiments with identical SST.  Having a prescribed SST warm 
patch ensures that the simulations will be `aggregated' to some degree.  
Given identical SSTs, the  range of different SFs provide a measure of variability that is driven entirely by the interactions between 
convection, radiation, and the large-scale circulation.

@@

\begin{figure}
    \includegraphics[width=0.95\columnwidth]{walkerfigs/hov_precip_lwoff_huge.eps}
  \caption{Identical to previous figure, except that the clouds do not interact with the longwave radiation; the LWCRE is off.}
  \label{fig:domdep_lwoff}
\end{figure}

%\begin{figure}
%  \centering
%       \includegraphics[width=0.45\columnwidth]{walkerfigs/Cond_Walker_P100vsP25_lgvsm_lwoff.eps}
%          \caption{Domain mean total condensate (liquid + ice; grams/kilogram) for P100 (red) and P25 (yellow) on the domain 
%          with a long dimension of 16,000km (thick) and 4,000 (thin).  Solid lines show experiments with LWCRE on
%          and dashed lines the LWCRE-off experiments.}
%  \label{fig:TotCond_P25P100}
%\end{figure}
\begin{figure}
  \centering
       \includegraphics[width=0.90\columnwidth]{DomainMeanCond_SinglePanel.pdf}
          \caption{Domain mean total condensate (liquid + ice; grams/kilogram) on the domain with a long dimension of 16,000km (a.)
          and 4,000 km (b.).  P25 experiments are shown with yellow lines and P100 experiments with red.  Solid lines show 
          experiments with LWCRE on and dashed lines the LWCRE-off experiments.}
  \label{fig:TotCond_P25P100}
\end{figure}

>>>>

The Walker circulation connects the regions with deep atmospheric convection in the western tropical Pacific to the shallow-convection, tropospheric subsidence, and stratocumulus cloud decks of the eastern Pacific.  Although important to many elements of the Earth system such as tropical precipitation, and cloud feedback processes, interactions between large-scale tropical circulations and these cloud systems are still not well understood.   The purpose of this study is to better understand the multi-scale interactions between the Walker circulation, cloud systems, and interactive radiation.  
To do this we simulate a mock-Walker Circulation with a full-physics General Circulation Model (GCM) using idealized boundary conditions.  Our experiments use a doubly-periodic domain with grid-spacing of 1, 2, 25, and 100km.  We thus span the range from General Circulation Models (GCMs) to Cloud-system Resolving Models (CRMs).  Our model is derived from the Geophysical Fluid Dynamics Laboratory (GFDL) atmospheric GCM (AM4.0).  \change[LGS]{Our GCM-like experiments have a large low-level cloud fraction while the CRM-like experiments have more upper-level clouds.}{We find substantial differences in the mock-Walker simulated by our GCM-like and CRM-like experiments.  The CRM-like experiments have more upper level clouds, stronger overturning circulations, and more precipitation.  The GCM-like experiments have a low-level cloud fraction that is up to 20\% larger.}
These differences lead to opposite atmospheric responses to changes in the longwave cloud radiative effect (LWCRE).  Active LWCRE lead to increased precipitation for our GCMs, but decreased precipitation for our CRMs.  The LWCRE leads to a narrower rising branch of the circulation and substantially increases the fraction of precipitation from the large-scale cloud parameterization.  \remove[LGS]{Decreasing the grid-spacing to 1km and 2km results in stronger overturning circulations, more condensate aloft, and less precipitation.}  This work demonstrates that a mock-Walker circulation is a useful generalization of RCE that includes a large-scale circulation.

%We find substantial differences in the mock-Walker simulated by our GCM-like and CRM-like experiments.  The CRM-like experiments have more upper level clouds, stronger overturning circulations, and more precipitation.  The GCM-like experiments have a low-level cloud fraction that is up to 20\% larger.

@@

\subsection{\add[LGS]{General Characteristics of the mock-WalkerCirculation}}

@@

When the coupling between the circulation and clouds is broken by making the clouds invisible to the 
LW radiation, the atmospheric state is more symmetric about the maximum SST and the weaker circulation
is more spread out horizontally.   
\note[LGS]{The following lines, which appear to have been deleted have been moved to subsection 3.2 and 
slightly rewritten for clarity.}
\remove[LGS]{The mass streamfunction and vertical velocity both show the 
P25 (Figure }\ref{fig:rh_psi_P25vsE25}, 
\change[LGS]{left panels}{a,d}; Figure \ref{fig:precip_vertvel})
\remove[LGS]{ experiment to have 
a stronger, more concentrated overturning circulation than either the P25 LWCRE-off (Figure} 
\ref{fig:rh_psi_P25vsE25} 
\remove[LGS]{b,e) or E25 (Figure} 
\ref{fig:rh_psi_P25vsE25} 
\remove[LGS]{c,f) experiments.   
The control GCM-like experiment (P25) also has higher RH and more condensate in the convective
region and a dryer subsidence region, relative to the P25 LWCRE-off and E25 experiments. 
Averaged over the full domain, the P25 case with parameterized convection results in a dryer atmosphere with less condensate (both liquid and ice).}
\change[LGS]{This}{The} default configuration in which the clouds interact with the LW radiation results in a stronger,
spatially concentrated circulation and will be discussed further in later sections (also seen Figures 4, 5, 9 and 10).
Active LWCRE leads to lower values of domain mean OLR and higher domain mean precipitable water (PW) in all cases (Table \ref{tab:experimentmeans}).

\begin{figure}
  \centering
      \includegraphics[width=0.8\columnwidth]{walkerfigs/PrecipVertVelocity_LWCRE_onoff.eps}
  \caption{Precipitation (a.,b.) and vertical velocity (c.,d.) at approximately 530 hPa for P100, P25, E2, and E1 experiments.  
  The data have been averaged over the short horizontal dimension of the channel and over the 
  equilibrated part of the experiments.  Panels a. and b. show the control configurations with default model physics. 
  Panels b. and d. show the corresponding experiments with the longwave cloud radiative effect turned
  off (LWCRE-off).}
  \label{fig:precip_vertvel}
\end{figure}

@@

@@

\note[LGS]{This paragraph was originally on lines 326-343 but has been moved to accommodate the reorganization of section 3.}
One of the simplest measures of convective aggregation and the large-scale circulation is the subsidence fraction (SF), the fraction of the domain 
in which the mid-tropospheric air is subsiding \cite{Coppin_Bony_2015}.  
As convection becomes more organized, or aggregated, the SF will increase.  For an overturning circulation a contraction of the convective 
region should result in a larger subsidence fraction.  
This is precisely what we see in Table \ref{tab:experimentmeans}.  For each of our experiments with LWCRE-on the SF is larger than 
or equal to the case with LWCRE-off \remove[LGS]{(with the exception of E25)}.   
While our mock-Walker circulation is distinct from radiative convective equilibrium (RCE) and the resulting spontaneous self-aggregation, our 
region of persistent deep convection clearly corresponds to a state of aggregation. 
Using a mock-Walker circulation allows one to study controlled convective aggregation rather then spontaneous convective self-aggregation. 
Previous studies have shown a dependence of aggregation 
on temperature \cite{Khairoutdinov2010, Wing2014, Cronin2017}, Table \ref{tab:experimentmeans} illustrates how much the aggregated 
state can vary among experiments with identical SST.  Having a prescribed SST warm 
patch ensures that the simulations will be `aggregated' to some degree.  
Given identical SSTs, the  range of different SFs provide a measure of variability that is driven entirely by the interactions between 
convection, radiation, and the large-scale circulation.

\subsection{\add[LGS]{Comparison of Experiments with Parameterized or Explicit Convection}}

Before analyzing the CRM-like experiments E1 and E2 in which there is no parameterized convection we examine the influence of 
the double plume convective parameterization in the P25 and P100 experiments.  The E25 experiment, identical to P25 except with 
fully explicit convection, then can serve as a link between the GCM-like experiments and the CRM-like experiments.

The mass streamfunction and vertical velocity both show the P25 (Figure \ref{fig:rh_psi_P25vsE25}, a,d; Figure \ref{fig:precip_vertvel}) experiment to have 
a stronger, more concentrated overturning circulation than either the P25 LWCRE-off (Figure \ref{fig:rh_psi_P25vsE25} b,e) or E25 (Figure 
\ref{fig:rh_psi_P25vsE25} c,f) experiments.   The control GCM-like experiment (P25) also has larger values of RH and more condensate in the convective
region and a dryer subsidence region, relative to the P25 LWCRE-off and E25 experiments. 
Averaged over the full domain, the P25 case with parameterized convection results in a dryer atmosphere with less condensate 
(Figure \ref{fig:profiles_P100P25E25} a.,b.).  Mean relative humidity profiles from the regions with 
mid-tropospheric subsidence (Figure \ref{fig:profiles_P100P25E25} a., dashed lines) further accentuate the dryness of P100 and P25 relative
to E25.

\begin{figure}
  \centering
      \includegraphics[width=0.95\columnwidth]{walkerfigs/MeanStructure_P100P25E25.eps}
  \caption{Domain mean vertical structure of the P100, P25, and E25 experiments.  The dashed lines of relative humidity (a.) show the values 
  in the region with subsidence.  The positive heating profiles (d.) show the heating due to both convection and the large-scale cloud scheme, the negative
  profiles show the sum of the heating due to longwave and shortwave radiation.  Panel e. shows the atmospheric temperature relative to the P100 experiment.}
  \label{fig:profiles_P100P25E25}
\end{figure}

The influence of different grid-spacing, and convective parameterization can be seen in the vertical profiles of several key variables for 
the P100, P25, and E25 experiments (Figure \ref{fig:profiles_P100P25E25} b.).  
Overall the experiments with parameterized convection transport more moisture (both condensate and water vapor)
out of the boundary layer and into the lower troposphere.  The parameterized experiments are also substantially warmer in the mid-troposphere compared to 
the E25 experiment which is forced to transport all moisture and heat with explicit dynamical motions.  In contrast, near 900 hPa, the E25 experiment has nearly twice
as much low-level condensate (Figure \ref{fig:profiles_P100P25E25} b.), a cloud fraction that is about 10 \% higher, larger condensational heating, and 
stronger cloud-top radiative cooling.  It is also worth noting that the condensational heating above 850 hPa (Figure \ref{fig:profiles_P100P25E25} d.) is dominated by 
the large-scale cloud scheme rather than the convective parameterization.  This is presumably because of the large-scale overturning circulation that is 
being forced by the SST pattern.  Overturning circulations tend to trigger the large-scale cloud scheme.  The fraction of precipitation that is due to either 
the large-scale or convective parameterizations will be discussed in the next section.

Figure \ref{fig:rh_psi_P25vsE25} suggests that the strong asymmetries of the circulation, moisture fields, and precipitation in P25 could be eliminated 
by either turning off the convective parematerization (E25) or by turning off the LWCRE.  Examining the evolving structure of the 
precipitation (Hovm{\"o}ller diagrams) over the full 5 year simulations for P25, P25 LWCRE-off, E25, and E25 LWCRE-off offers more insight into the role of the convective parameterization and the CRE.

While the P25 experiment shows a fairly consistent irregularity (a.), both the P25 LWCRE-off (b.) and the E25 experiments (c.) have distinct patterns that 
can remain steady for years before changing.  In contrast to the precipitation structures in panels a,b, and c of Figure \ref{fig:hov_25km_4pan}, the E25 LWCRE-off experiment 
shows (d.) a zipper-like structure of strong precipitation that persists throughout the entire 5 years of the experiment.

%The patterns of precipitation in Figure \ref{fig:hov_25km_4pan} show an asymmetric and sporadic evolution in time as well as an oscillating pattern that is remarkably steady 
%in time.

\begin{figure}
  \centering
      \includegraphics[width=0.95\columnwidth]{walkerfigs/hov_precip_25km4pan_huge.eps}
  \caption{Evolution of precipitation through 5 years of simulation for four experiments with a grid spacing of
  25km.  Panel a shows the  control 25km experiment (P25); 
  panel b, P25 with LWCRE turned off; panel c, both deep and shallow convective parameterization schemes are turned off (E25); 
  and panel d shows the E25 experiment shown in panel c except with the LWCRE turned off.  
  All cases have an SST of 301 K at the center and 297K at the edges.  
  The plotted contour values are: 1,5,10,15,20,30,40,50,60,70,80,90.  Data have been averaged over the short horizontal dimension.}
  \label{fig:hov_25km_4pan}
\end{figure}

% discussing the asymmetry of P25 could/should lead into a discussion of Figure \ref{fig:hov_25km_4pan}...

One of the most prominent features of our GCM-like simulations is \change[LGS]{an asymmetry (relative to the 
symmetric SST distribution) in both the time-dependent and steady-state solutions}{the erratic (relative to the symmetric SST distribution) 
structure of the precipitation field}.  
This \remove[LGS]{asymmetry} is particularly apparent in the P25 experiment on the small domain but is also present on larger domains and 
with a grid-spacing of $100 \, \rm{km}$ (Figures  \ref{fig:precip_vertvel}, \ref{fig:domdep} and  \ref{fig:conv_vs_ls}). 
The steady-state precipitation maximum is located  not over the warmest SST but is shifted to slightly cooler temperatures.  
This asymmetry is present in the vertical velocity, mass circulation, relative humidity, specific humidity, and radiative heating.  
In the Hovm{\"o}ller diagrams (Figures \ref{fig:domdep} and \ref{fig:domdep_lwoff}), the precipitation appears to be averse 
to residing over the SST maximum.  
For the P25 case shown in Figure \ref{fig:rh_psi_P25vsE25} a strong ($1 \, \rm{m \, s^{-1}}$) domain
mean shear develops above about 500 m which shifts the precipitation and circulation off center for years at a time.  
When the convective parameterization is turned off (E25), the overturning circulation 
becomes weaker and broader (seen in vertical velocity, and the mass streamfunction, Figures \ref{fig:rh_psi_P25vsE25} and \ref{fig:precip_vertvel}), 
and the precipitation, cloud fields, and circulation reside over the SST maximum (but only for about 1 year before the variability 
increases).    
While the parameterized convection plays a large role in driving this asymmetry, it is not purely a 
result of the convective parameterization, but also due to an interaction between the convective 
parameterization and the LWCRE.   The degree to which this asymmetry influences the comparison with other 
experiments is unclear.

%
% below shows that the circulation extremes decrease when the lw cre is switched off.  the case with a 
% grid-spacing of 25 km shows the largest difference 
%
%% max/min values for the stream function with lwcre off:
%(0)	max/min of psiplot ensind  is: 0.3477345977293868 and: -0.2115510906212598   diff = 0.56
%(0)	max/min of psiplot1 is: 0.3195050101301776 and: -0.2795603759630235             diff = 0.60
%(0)	max/min of psiplot2 is: 0.3551683771471268 and: -0.3245916357825396             diff = 0.68
%
%% max/min values for the stream function with lwcre on:
%(0)	max/min of psiplot ensind  is: 0.1346705118433919 and: -0.6774837967222883    diff = 0.81
%(0)	max/min of psiplot1 is: 0.301707822836468 and: -0.3661587052771586                diff = 0.67
%(0)	max/min of psiplot2 is: 0.4634904466711686 and: -0.3170573366946793               diff = 0.78

@@

\begin{figure}
    \includegraphics[width=0.95\columnwidth]{walkerfigs/hov_precip_lwoff_huge.eps}
  \caption{Identical to Figure \ref{fig:domdep}, except that the clouds do not interact with the longwave radiation; the LWCRE is off.}
  \label{fig:domdep_lwoff}
\end{figure}

%\begin{figure}
%  \centering
%       \includegraphics[width=0.45\columnwidth]{walkerfigs/Cond_Walker_P100vsP25_lgvsm_lwoff.eps}
%          \caption{Domain mean total condensate (liquid + ice; grams/kilogram) for P100 (red) and P25 (yellow) on the domain 
%          with a long dimension of 16,000km (thick) and 4,000 (thin).  Solid lines show experiments with LWCRE on
%          and dashed lines the LWCRE-off experiments.}
%  \label{fig:TotCond_P25P100}
%\end{figure}
\begin{figure}
  \centering
       \includegraphics[width=0.90\columnwidth]{DomainMeanCond_SinglePanel.pdf}
          \caption{Domain mean total condensate (liquid + ice; grams/kilogram) on the domain with a long dimension of 4,000km (a.)
          and 16,000 km (b.).  P25 experiments are shown with yellow lines and P100 experiments with red.  Solid lines show 
          experiments with LWCRE on and dashed lines the LWCRE-off experiments.}
  \label{fig:TotCond_P25P100}
\end{figure}
